---
title: "LCLUC_INTRA_category_analyses"
author: "Jessie Dearing"
date: "2025-08-04"
output: pdf_document
---

This relies on the combined dfs from 1_data_import.

```{r setup , include = FALSE}
library(kableExtra)
library(ggplot2)
library(janitor)
library(skimr)
library(tidyr)
library(tidyverse)
library(dplyr)
library(purrr)
```

```{r setup, include=FALSE}
# Source the script that creates `base_`
source("1_data_import.R")  # Replace with the actual script filename

# Now `base_` should exist before calling skim()
if (exists("base_")) {
  skim(base_)
}
```

```{r, include=FALSE}

#setwd("C:/Users/jessi/OneDrive - Cornell University/Documents/MSPhD/AllingtonLab_LCLUC/RStudio_WorkingDirectory")
names(base_) <- gsub("\\.x$", "", names(base_))

str(base_)
base_ <- as.data.frame(base_)
base_ <- base_ %>% 
  mutate(across(Ref, as.factor))
```


# I. LABOR

## 3A vs. 4A ---------------------------------------------------------------------
#### Who in the family undertake migrations? vs. Does migration impact labor?
#### Columns: labor_whoMigrates/labor_migImpactLabor
```{r, echo=FALSE}
labor_long <- base_LABOR %>%
  select(labor_whoMigrates, labor_migImpactLabor) %>%
  filter(!is.na(labor_whoMigrates)) %>%
  mutate(
    labor_whoMigrates = str_replace(labor_whoMigrates, "Husband. 2 sons", "husband, sons")
  ) %>%
  separate_rows(labor_whoMigrates, sep = ",") %>%
  mutate(
    labor_whoMigrates = str_trim(str_to_lower(labor_whoMigrates)),
    labor_whoMigrates = case_when(
      labor_whoMigrates == "grandparents" ~ "grandparent(s), unspecified",
      labor_whoMigrates == "grandmother" ~ "grandparent(s), unspecified",
      labor_whoMigrates == "child" ~ "child(ren), unspecified",
      labor_whoMigrates == "children" ~ "child(ren), unspecified",
      labor_whoMigrates == "son" ~ "son(s)",
      labor_whoMigrates == "2 sons" ~ "son(s)",
      labor_whoMigrates == "3 sons" ~ "son(s)",
      labor_whoMigrates == "son (student)" ~ "son(s)",
      labor_whoMigrates == "son (when he is available)" ~ "son(s)",
      labor_whoMigrates == "son 2" ~ "son(s)",
      labor_whoMigrates == "olders son comes to help" ~ "son(s)",
      labor_whoMigrates == "sons" ~ "son(s)",
      labor_whoMigrates == "daughter" ~ "daughter(s)",
      labor_whoMigrates == "1 daughter" ~ "daughter(s)",
      labor_whoMigrates == "2 daughters" ~ "daughter(s)",
      labor_whoMigrates == "2 children" ~ "child(ren), unspecified",
      labor_whoMigrates == "3 children" ~ "child(ren), unspecified",
      labor_whoMigrates == "4 children" ~ "child(ren), unspecified",
      labor_whoMigrates == "7 children" ~ "child(ren), unspecified",
      labor_whoMigrates == "older brother" ~ "brother(s)",
      labor_whoMigrates == "older brothers help" ~ "brother(s)",
      labor_whoMigrates == "sibling" ~ "sibling(s), unspecified",
      labor_whoMigrates == "siblings" ~ "sibling(s), unspecified",
      labor_whoMigrates == "2 younger siblings" ~ "sibling(s), unspecified",
      labor_whoMigrates == "3 siblings-neighbors" ~ "sibling(s), unspecified",
      labor_whoMigrates == "4 younger siblings" ~ "sibling(s), unspecified",
      labor_whoMigrates == "younger sibling" ~ "sibling(s), unspecified",
      labor_whoMigrates == "younger siblings 2" ~ "sibling(s), unspecified",
      labor_whoMigrates == "grandchild" ~ "grandchild(ren), unspecified",
      labor_whoMigrates == "grandchildren" ~ "grandchild(ren), unspecified",
      labor_whoMigrates == "grandchidlren" ~ "grandchild(ren), unspecified",
      labor_whoMigrates == "1" ~ "person(s), unspecified",
      labor_whoMigrates == "2" ~ "person(s), unspecified",
      labor_whoMigrates == "3" ~ "person(s), unspecified",
      labor_whoMigrates == "4" ~ "person(s), unspecified",
      labor_whoMigrates == "4 people" ~ "person(s), unspecified",
      labor_whoMigrates == "24" ~ "person(s), unspecified",
      labor_whoMigrates == "3-feb" ~ "person(s), unspecified",
      labor_whoMigrates == "6 people" ~ "person(s), unspecified",
      labor_whoMigrates == "everyone 3" ~ "person(s), unspecified",
      labor_whoMigrates == "everyone" ~ "person(s), unspecified",
      labor_whoMigrates == "neighbors" ~ "friend/neighbor(s)",
      labor_whoMigrates == "3 neighbors" ~ "friend/neighbor(s)",
      labor_whoMigrates == "2 neighbors" ~ "friend/neighbor(s)",
      labor_whoMigrates == "4 neighbors" ~ "friend/neighbor(s)",
      labor_whoMigrates == "neighbors 4" ~ "friend/neighbor(s)",
      labor_whoMigrates == "friends" ~ "friend/neighbor(s)",
      labor_whoMigrates == "daughter-in-law" ~ "extended family/in-laws",
      labor_whoMigrates == "son-in-law" ~ "extended family/in-laws",
      labor_whoMigrates == "father-in-law" ~ "extended family/in-laws",
      labor_whoMigrates == "brother-in-law" ~ "extended family/in-laws",
      labor_whoMigrates == "extended family members" ~ "extended family/in-laws",
      labor_whoMigrates == "herder children's families" ~ "extended family/in-laws",
      labor_whoMigrates == "in soum" ~ "extended family/in-laws",
      labor_whoMigrates == "school children" ~ "extended family/in-laws",
      labor_whoMigrates == "wide" ~ "extended family/in-laws",
      labor_whoMigrates == "younger brother and his wife" ~ "extended family/in-laws",
      labor_whoMigrates == "extended families" ~ "extended family/in-laws",
      labor_whoMigrates == "assistant herder" ~ "hired help",
      labor_whoMigrates == "herders 4" ~ "hired help",
      labor_whoMigrates == "50 year old" ~ "other",
      labor_whoMigrates == "ask for help" ~ "other",
      labor_whoMigrates == "ask someone for help" ~ "other",
      labor_whoMigrates == "don't move" ~ "other",
      labor_whoMigrates == "me" ~ "just myself",
      labor_whoMigrates == "0" ~ "just myself",
      labor_whoMigrates == "others" ~ "other",
      TRUE ~ labor_whoMigrates
    ),
    labor_migImpactLabor = str_trim(str_to_lower(labor_migImpactLabor)),
    labor_migImpactLabor = case_when(
      labor_migImpactLabor %in% c("yes", "y", "1", "true") ~ "Yes",
      labor_migImpactLabor %in% c("no", "n", "0", "false") ~ "No",
      is.na(labor_migImpactLabor) ~ NA_character_,
      TRUE ~ str_to_title(labor_migImpactLabor)
    )
  )

impact_by_member <- labor_long %>%
  group_by(labor_whoMigrates, labor_migImpactLabor) %>%
  summarise(n = n(), .groups = "drop_last") %>%
  mutate(total = sum(n), pct = n / total) %>%
  ungroup() %>%
  arrange(labor_whoMigrates, desc(labor_migImpactLabor))

count_overall <- labor_long %>%
  count(labor_whoMigrates, name = "total_mentions")

impact_wide <- impact_by_member %>%
  filter(labor_migImpactLabor %in% c("Yes", "No")) %>%
  select(labor_whoMigrates, impact = labor_migImpactLabor, n) %>%
  tidyr::pivot_wider(names_from = impact, values_from = n, values_fill = 0) %>%
  mutate(pct_yes = if_else(Yes + No > 0, Yes / (Yes + No), NA_real_)) %>%
  left_join(count_overall, by = "labor_whoMigrates") %>%
  arrange(desc(pct_yes), desc(total_mentions))

kable(impact_wide, n = 200)
```


## 3A vs 4B ---------------------------------------------------------------------
#### Who in the family undertake migrations? vs. Does migration impact herding practices?
#### Columns: labor_whoMigrates/labor_migImpactPract
```{r, echo=FALSE}
labor_long <- base_LABOR %>%
  select(labor_whoMigrates, labor_migImpactPract) %>%
  filter(!is.na(labor_whoMigrates)) %>%
  mutate(
    labor_whoMigrates = str_replace(labor_whoMigrates, "Husband. 2 sons", "husband, sons")
  ) %>%
  separate_rows(labor_whoMigrates, sep = ",") %>%
  mutate(
    labor_whoMigrates = str_trim(str_to_lower(labor_whoMigrates)),
    labor_whoMigrates = case_when(
      labor_whoMigrates == "grandparents" ~ "grandparent(s), unspecified",
      labor_whoMigrates == "grandmother" ~ "grandparent(s), unspecified",
      labor_whoMigrates == "child" ~ "child(ren), unspecified",
      labor_whoMigrates == "children" ~ "child(ren), unspecified",
      labor_whoMigrates == "son" ~ "son(s)",
      labor_whoMigrates == "2 sons" ~ "son(s)",
      labor_whoMigrates == "3 sons" ~ "son(s)",
      labor_whoMigrates == "son (student)" ~ "son(s)",
      labor_whoMigrates == "son (when he is available)" ~ "son(s)",
      labor_whoMigrates == "son 2" ~ "son(s)",
      labor_whoMigrates == "olders son comes to help" ~ "son(s)",
      labor_whoMigrates == "sons" ~ "son(s)",
      labor_whoMigrates == "daughter" ~ "daughter(s)",
      labor_whoMigrates == "1 daughter" ~ "daughter(s)",
      labor_whoMigrates == "2 daughters" ~ "daughter(s)",
      labor_whoMigrates == "2 children" ~ "child(ren), unspecified",
      labor_whoMigrates == "3 children" ~ "child(ren), unspecified",
      labor_whoMigrates == "4 children" ~ "child(ren), unspecified",
      labor_whoMigrates == "7 children" ~ "child(ren), unspecified",
      labor_whoMigrates == "older brother" ~ "brother(s)",
      labor_whoMigrates == "older brothers help" ~ "brother(s)",
      labor_whoMigrates == "sibling" ~ "sibling(s), unspecified",
      labor_whoMigrates == "siblings" ~ "sibling(s), unspecified",
      labor_whoMigrates == "2 younger siblings" ~ "sibling(s), unspecified",
      labor_whoMigrates == "3 siblings-neighbors" ~ "sibling(s), unspecified",
      labor_whoMigrates == "4 younger siblings" ~ "sibling(s), unspecified",
      labor_whoMigrates == "younger sibling" ~ "sibling(s), unspecified",
      labor_whoMigrates == "younger siblings 2" ~ "sibling(s), unspecified",
      labor_whoMigrates == "grandchild" ~ "grandchild(ren), unspecified",
      labor_whoMigrates == "grandchildren" ~ "grandchild(ren), unspecified",
      labor_whoMigrates == "grandchidlren" ~ "grandchild(ren), unspecified",
      labor_whoMigrates == "1" ~ "person(s), unspecified",
      labor_whoMigrates == "2" ~ "person(s), unspecified",
      labor_whoMigrates == "3" ~ "person(s), unspecified",
      labor_whoMigrates == "4" ~ "person(s), unspecified",
      labor_whoMigrates == "4 people" ~ "person(s), unspecified",
      labor_whoMigrates == "24" ~ "person(s), unspecified",
      labor_whoMigrates == "3-feb" ~ "person(s), unspecified",
      labor_whoMigrates == "6 people" ~ "person(s), unspecified",
      labor_whoMigrates == "everyone 3" ~ "person(s), unspecified",
      labor_whoMigrates == "everyone" ~ "person(s), unspecified",
      labor_whoMigrates == "neighbors" ~ "friend/neighbor(s)",
      labor_whoMigrates == "3 neighbors" ~ "friend/neighbor(s)",
      labor_whoMigrates == "2 neighbors" ~ "friend/neighbor(s)",
      labor_whoMigrates == "4 neighbors" ~ "friend/neighbor(s)",
      labor_whoMigrates == "neighbors 4" ~ "friend/neighbor(s)",
      labor_whoMigrates == "friends" ~ "friend/neighbor(s)",
      labor_whoMigrates == "daughter-in-law" ~ "extended family/in-laws",
      labor_whoMigrates == "son-in-law" ~ "extended family/in-laws",
      labor_whoMigrates == "father-in-law" ~ "extended family/in-laws",
      labor_whoMigrates == "brother-in-law" ~ "extended family/in-laws",
      labor_whoMigrates == "extended family members" ~ "extended family/in-laws",
      labor_whoMigrates == "herder children's families" ~ "extended family/in-laws",
      labor_whoMigrates == "in soum" ~ "extended family/in-laws",
      labor_whoMigrates == "school children" ~ "extended family/in-laws",
      labor_whoMigrates == "wide" ~ "extended family/in-laws",
      labor_whoMigrates == "younger brother and his wife" ~ "extended family/in-laws",
      labor_whoMigrates == "extended families" ~ "extended family/in-laws",
      labor_whoMigrates == "assistant herder" ~ "hired help",
      labor_whoMigrates == "herders 4" ~ "hired help",
      labor_whoMigrates == "50 year old" ~ "other",
      labor_whoMigrates == "ask for help" ~ "other",
      labor_whoMigrates == "ask someone for help" ~ "other",
      labor_whoMigrates == "don't move" ~ "other",
      labor_whoMigrates == "me" ~ "just myself",
      labor_whoMigrates == "0" ~ "just myself",
      labor_whoMigrates == "others" ~ "other",
      TRUE ~ labor_whoMigrates
    ),
    labor_migImpactPract = str_trim(str_to_lower(labor_migImpactPract)),
    labor_migImpactPract = case_when(
      labor_migImpactPract %in% c("yes", "y", "1", "true") ~ "Yes",
      labor_migImpactPract %in% c("no", "n", "0", "false") ~ "No",
      is.na(labor_migImpactPract) ~ NA_character_,
      TRUE ~ str_to_title(labor_migImpactPract)  # keeps values like "Don't know"
    )
  )

impact_by_member2 <- labor_long %>%
  group_by(labor_whoMigrates, labor_migImpactPract) %>%
  summarise(n = n(), .groups = "drop_last") %>%
  mutate(total = sum(n), pct = n / total) %>%
  ungroup() %>%
  arrange(labor_whoMigrates, desc(labor_migImpactPract))

count_overall <- labor_long %>%
  count(labor_whoMigrates, name = "total_mentions")

impact_wide2 <- impact_by_member2 %>%
  filter(labor_migImpactPract %in% c("Yes", "No")) %>%
  select(labor_whoMigrates, impact = labor_migImpactPract, n) %>%
  tidyr::pivot_wider(names_from = impact, values_from = n, values_fill = 0) %>%
  mutate(pct_yes = if_else(Yes + No > 0, Yes / (Yes + No), NA_real_)) %>%
  left_join(count_overall, by = "labor_whoMigrates") %>%
  arrange(desc(pct_yes), desc(total_mentions))

kable(impact_wide2, n = 200)
```


## 3B vs. 4A ---------------------------------------------------------------------
#### How many family members undertake migrations? vs. Does migration impact labor?
#### Columns: labor_numMigrates/labor_migImpactLabor
```{r, echo=FALSE}
num_vs_impact1 <- base_LABOR %>%
  select(labor_numMigrates, labor_migImpactLabor) %>%
  mutate(
    labor_numMigrates = readr::parse_number(as.character(labor_numMigrates)),
    labor_migImpactLabor = str_trim(str_to_lower(labor_migImpactLabor)),
    labor_migImpactLabor = case_when(
      labor_migImpactLabor %in% c("yes", "y", "1", "true") ~ "Yes",
      labor_migImpactLabor %in% c("no",  "n", "0", "false") ~ "No",
      is.na(labor_migImpactLabor) ~ NA_character_,
      TRUE ~ str_to_title(labor_migImpactLabor)
    )
  ) %>%
  filter(!is.na(labor_numMigrates))

impact_by_number1 <- num_vs_impact1 %>%
  group_by(labor_numMigrates, labor_migImpactLabor) %>%
  summarise(n = n(), .groups = "drop_last") %>%
  mutate(total = sum(n), pct = n / total) %>%
  ungroup() %>%
  arrange(labor_numMigrates, desc(labor_migImpactLabor))

kable(impact_by_number1, n = 200)
```


## 3B vs. 4B ---------------------------------------------------------------------
#### How many family members undertake migrations? vs. Does migration impact herding practices?
#### Columns: labor_numMigrates/labor_migImpactPract
```{r, echo=FALSE}
num_vs_impact2 <- base_LABOR %>%
  select(labor_numMigrates, labor_migImpactPract) %>%
  mutate(
    labor_numMigrates = readr::parse_number(as.character(labor_numMigrates)),
    labor_migImpactPract = str_trim(str_to_lower(labor_migImpactPract)),
    labor_migImpactPract = case_when(
      labor_migImpactPract %in% c("yes", "y", "1", "true") ~ "Yes",
      labor_migImpactPract %in% c("no",  "n", "0", "false") ~ "No",
      is.na(labor_migImpactPract) ~ NA_character_,
      TRUE ~ str_to_title(labor_migImpactPract)
    )
  ) %>%
  filter(!is.na(labor_numMigrates))

impact_by_number2 <- num_vs_impact2 %>%
  group_by(labor_numMigrates, labor_migImpactPract) %>%
  summarise(n = n(), .groups = "drop_last") %>%
  mutate(total = sum(n), pct = n / total) %>%
  ungroup() %>%
  arrange(labor_numMigrates, desc(labor_migImpactPract))

kable(impact_by_number2, n = 200)
```


## 3A vs. 5A ---------------------------------------------------------------------
#### How many people undertake migrations? vs. Do you hire labor?
#### Columns: labor_whoMigrates/labor_hire
```{r, echo=FALSE}
num_vs_impact3 <- base_LABOR %>%
  select(labor_numMigrates, labor_hire) %>%
  mutate(
    labor_numMigrates = readr::parse_number(as.character(labor_numMigrates)),
    labor_hire = str_trim(str_to_lower(labor_hire)),
    labor_hire = case_when(
      labor_hire %in% c("yes", "y", "1", "true") ~ "Yes",
      labor_hire %in% c("no",  "n", "0", "false") ~ "No",
      is.na(labor_hire) ~ NA_character_,
      TRUE ~ str_to_title(labor_hire)
    )
  ) %>%
  filter(!is.na(labor_numMigrates))

impact_by_number3 <- num_vs_impact3 %>%
  group_by(labor_numMigrates, labor_hire) %>%
  summarise(n = n(), .groups = "drop_last") %>%
  mutate(total = sum(n), pct = n / total) %>%
  ungroup() %>%
  arrange(labor_numMigrates, desc(labor_hire))

kable(impact_by_number3, n = 200)
```
--------------------------------------------------------------------------------
--------------------------------------------------------------------------------





# II. ALTERNATIVE LIVELIHOODS

## 1A vs. 3A---------------------------------------------------------------------
#### Is someone in the household doing non-herding work?  vs. Number of loans taken out per year?
#### Columns: altLife_nonHerdWork/altLife_loansPerYr
```{r, echo=FALSE}
nonHerd_loans <- base_ALTLIFE %>%
  select(altLife_loansPerYr, altLife_nonHerdWork) %>%
  mutate(
    altLife_loansPerYr = readr::parse_number(as.character(altLife_loansPerYr)),
    altLife_nonHerdWork = str_trim(str_to_lower(altLife_nonHerdWork)),
    altLife_nonHerdWork = case_when(
      altLife_nonHerdWork %in% c("yes", "y", "1", "true") ~ "Yes",
      altLife_nonHerdWork %in% c("no",  "n", "0", "false") ~ "No",
      is.na(altLife_nonHerdWork) ~ NA_character_,
      TRUE ~ str_to_title(altLife_nonHerdWork)
    )
  ) %>%
  filter(!is.na(altLife_loansPerYr))

nonHerd_loans <- nonHerd_loans %>%
  group_by(altLife_loansPerYr, altLife_nonHerdWork) %>%
  summarise(n = n(), .groups = "drop_last") %>%
  mutate(total = sum(n), pct = n / total) %>%
  ungroup() %>%
  arrange(altLife_loansPerYr, desc(altLife_nonHerdWork))

kable(nonHerd_loans, n = 200)
```


## 1A vs. 3C---------------------------------------------------------------------
#### Is someone in the household doing non-herding work?  vs. When do you typically need loans?
#### Columns: altLife_nonHerdWork/altLife_loansWhenNeed
```{r, echo=FALSE}
count_loansWhenNeed <- base_ALTLIFE %>%
  select(altLife_loansWhenNeed, altLife_nonHerdWork) %>%
  filter(!is.na(altLife_loansWhenNeed)) %>%
  mutate(
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "Winter and spring", "winter, spring"),
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "Winter and Spring", "winter, spring"),
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "august- for school year and lunar new year", "autumn, lunar new year"),
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "Winter-fodder", "winter"),
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "winter-fodder", "winter"),
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "Winter- require fodder", "winter"),
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "and Winter", "winter"),
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "winter and petrol", "winter"),
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "february", "winter"),
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "February", "winter"),
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "After December", "winter"),
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "Winter and preparation of fodder", "winter"),
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "Dec", "winter"),
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "december", "winter"),
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "winter-winter for fodder", "winter"),
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "winterember", "winter"),
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "Winter Nov-March", "winter"),
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "winter and spring", "winter, spring"),
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "winter and Lunar new year", "winter, lunar new year"),
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "Winter and Lunar new year", "winter, lunar new year"),
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "Winter and Lunar New Year", "winter, lunar new year"),
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "spring and autumn", "spring, autumn"),
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "spring-fodder", "spring"),
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "Spring- before cashmere collection", "spring"),
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "Lunar new year-spring", "spring, lunar new year"),
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "summer and winter", "summer, winter"),
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "Sep-fodder", "autumn"),
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "autumn-fodder", "autumn"),
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "prepare fodder in Autumn", "autumn"),
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "August", "autumn"),
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "Autumn- school year", "autumn"),
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "Autumn- school new year", "autumn"),
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "Aug", "autumn"),
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "autumn-sep", "autumn"),
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "Autumn-sep", "autumn"),
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "October", "autumn"),
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "September", "autumn"),
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "Autumn- student tuition fee payment and buying fodder", "autumn"),
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "Autumn- school year starts", "autumn"),
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "september-school year", "autumn"),
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "Autumn-school new year", "autumn"),
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "Autumn-school year starts", "autumn"),
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "autumn -sep", "autumn"),
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "autumn- for school year and lunar new year", "autumn, lunar new year"),
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "Autumn and Lunar New Year", "autumn, lunar new year"),
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "autumn and during lunar new year", "autumn, lunar new year"),
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "Lunar New Year and Sept", "autumn, lunar new year"),
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "autumn and spring-lunar new year", "autumn, lunar new year, spring"),
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "Autum and winter", "autumn, winter"),
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "september and during harsh winter", "autumn, winter"),
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "autumn and winter", "autumn, winter"),
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "Lunar New year and need of fodder", "lunar new year"), 
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "If livestock is weak", "depends on needs"), 
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "depends on demands", "depends on needs"), 
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "0", "never"), 
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "None", "never"), 
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "one", "never"),
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "During migration and need of fodder", "during migration, depends on needs"), 
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "Autumn and during medical treatment", "autumn, during medical treatment")
  ) %>%
  separate_rows(altLife_loansWhenNeed, sep = ",") %>%
  mutate(
    altLife_loansWhenNeed = str_trim(altLife_loansWhenNeed),
    altLife_loansWhenNeed = str_to_lower(altLife_loansWhenNeed),
    altLife_nonHerdWork = str_trim(str_to_lower(altLife_nonHerdWork)),
    altLife_nonHerdWork = case_when(
      altLife_nonHerdWork %in% c("yes", "y", "1", "true") ~ "Yes",
      altLife_nonHerdWork %in% c("no", "n", "0", "false") ~ "No",
    is.na(altLife_nonHerdWork) ~ NA_character_,
  TRUE ~ str_to_title(altLife_nonHerdWork)  # keeps values like "Don't know"
)
)

  
count_loansWhenNeed <- count_loansWhenNeed %>%
  group_by(altLife_loansWhenNeed, altLife_nonHerdWork) %>%
  summarise(n = n(), .groups = "drop_last") %>%
  mutate(total = sum(n), pct = n / total) %>%
  ungroup() %>%
  arrange(altLife_loansWhenNeed, desc(altLife_nonHerdWork))

kable(count_loansWhenNeed, n = 200)
```
--------------------------------------------------------------------------------
--------------------------------------------------------------------------------





# III. HERD MANAGEMENT

## 5B vs. 9A---------------------------------------------------------------------
#### What is the average distance of moves, now vs. 10yrs ago?  vs. Changed management practices (yes/no):
#### Columns: herdMgmt_avgDistMoves/herdMgmt_10yrs_avgMoveDist/herdMgmt_past5Yrs_mgmtChanges
```{r, echo=FALSE}
herdMove_changePrac <- base_HERDMGMT %>%
  select(herdMgmt_10yrs_avgMoveDist, herdMgmt_avgDistMoves, herdMgmt_past5Yrs_mgmtChanges) %>%
  mutate(
    dist_10yrs = parse_number(as.character(herdMgmt_10yrs_avgMoveDist)),
    dist_now   = parse_number(as.character(herdMgmt_avgDistMoves)),
    move_diff  = dist_now - dist_10yrs,  # >0 means moved more now
    move_category = case_when(
      is.na(dist_10yrs) | is.na(dist_now) ~ NA_character_,
      move_diff > 0 ~ "moved less 10yrs ago than last year",
      move_diff < 0 ~ "moved more 10yrs ago than last year",
      TRUE ~ "moved an equal amount of distance"
    ),
    practices_chgd = str_trim(str_to_lower(herdMgmt_past5Yrs_mgmtChanges)),
    practices_chgd = case_when(
      practices_chgd %in% c("yes", "y", "1", "true") ~ "Yes",
      practices_chgd %in% c("no",  "n", "0", "false") ~ "No",
      is.na(practices_chgd) ~ NA_character_,
      TRUE ~ str_to_title(practices_chgd)
    )
  ) %>%
  filter(!is.na(move_category))

impact_by_movement <- herdMove_changePrac %>%
  group_by(move_category, practices_chgd) %>%
  summarise(n = n(), .groups = "drop_last") %>%
  mutate(total = sum(n), pct = n / total) %>%
  ungroup() %>%
  arrange(move_category, desc(practices_chgd))

kable(impact_by_movement, n = 200)
```

 
## 9A vs. 11A--------------------------------------------------------------------
#### Changed management practices (yes/no):  vs. Are there changes you want to make to your management practices but can’t?
#### Columns: herdMgmt_past5Yrs_mgmtChanges/herdMgmt_whatChanges_cantMake
```{r, echo=FALSE}
change_compare <- base_HERDMGMT %>%
  select(herdMgmt_past5Yrs_mgmtChanges, herdMgmt_whatChanges_cantMake) %>%
  mutate(
    past_made_changes = str_trim(str_to_lower(herdMgmt_past5Yrs_mgmtChanges)),
    past_made_changes = case_when(
      past_made_changes %in% c("yes", "y", "1", "true") ~ "Yes",
      past_made_changes %in% c("no", "n", "0", "false") ~ "No",
      TRUE ~ str_to_title(past_made_changes)
    ),
    future_cantChange = str_trim(str_to_lower(herdMgmt_whatChanges_cantMake)),
    future_cantChange = case_when(
      future_cantChange %in% c("yes", "y", "1", "true") ~ "Yes",
      future_cantChange %in% c("no", "n", "0", "false") ~ "No",
      TRUE ~ str_to_title(future_cantChange)
    )
  ) %>%
  count(past_made_changes, future_cantChange, sort = TRUE)
kable(change_compare)
```


## 10A vs. 12--------------------------------------------------------------------
#### Planning to change management practices (yes/no):  vs. Condition and degree of pastoral change:
#### Columns: herdMgmt_next5Yrs_mgmtChanges/herdMgmt_pastureCon_chg_yn/herdMgmt_pastureCon_chg_deg
```{r, echo=FALSE}
mgmt_next_vs_condition <- base_HERDMGMT %>%
  mutate(
    yn  = str_to_title(str_trim(herdMgmt_pastureCon_chg_yn)),
    deg = str_to_title(str_trim(herdMgmt_pastureCon_chg_deg)),
    condition_comparison = case_when(
      yn == "Degraded"  & deg == "Slight"      ~ "Slightly Degraded",
      yn == "Degraded"  & deg == "Medium"      ~ "Moderately Degraded",
      yn == "Degraded"  & deg == "Substantial" ~ "Substantially Degraded",
      yn == "Improved"  & deg == "Slight"      ~ "Slightly Improved",
      yn == "Improved"  & deg == "Medium"      ~ "Moderately Improved",
      yn == "Improved"  & deg == "Substantial" ~ "Substantially Improved",
      yn == "No Change"                        ~ "No change",
      TRUE ~ NA_character_
    ),
    next5yrs_changes = str_to_lower(str_trim(herdMgmt_next5Yrs_mgmtChanges)),
    next5yrs_changes = case_when(
      next5yrs_changes %in% c("yes", "y", "1", "true") ~ "Yes",
      next5yrs_changes%in% c("no",  "n", "0", "false") ~ "No",
      is.na(next5yrs_changes) ~ NA_character_,
      TRUE ~ str_to_title(next5yrs_changes)  # keeps "Don't know", etc.
    )
  )
condition_order <- c(
  "Substantially Degraded","Moderately Degraded","Slightly Degraded",
  "No change",
  "Slightly Improved","Moderately Improved","Substantially Improved"
)
mgmt_next_vs_condition <- mgmt_next_vs_condition %>%
  mutate(condition_comparison = factor(condition_comparison, levels = condition_order))

next5_by_condition <- mgmt_next_vs_condition %>%
  filter(!is.na(condition_comparison)) %>%
  group_by(condition_comparison, next5yrs_changes) %>%
  summarise(n = n(), .groups = "drop_last") %>%
  mutate(total = sum(n), pct = n / total) %>%
  ungroup() %>%
  arrange(condition_comparison, desc(next5yrs_changes))

kable(next5_by_condition, n = 200)
```


## 11A vs. 12--------------------------------------------------------------------
#### Are there changes you want to make to your management practices but can’t? vs. Condition and degree of pastoral change:
#### Columns: herdMgmt_whatChanges_cantMake/herdMgmt_pastureCon_chg_yn/herdMgmt_pastureCon_chg_deg
```{r, echo=FALSE}
chgDesire_vs_condition <- base_HERDMGMT %>%
  mutate(
    yn  = str_to_title(str_trim(herdMgmt_pastureCon_chg_yn)),
    deg = str_to_title(str_trim(herdMgmt_pastureCon_chg_deg)),
    condition_comparison = case_when(
      yn == "Degraded"  & deg == "Slight"      ~ "Slightly Degraded",
      yn == "Degraded"  & deg == "Medium"      ~ "Moderately Degraded",
      yn == "Degraded"  & deg == "Substantial" ~ "Substantially Degraded",
      yn == "Improved"  & deg == "Slight"      ~ "Slightly Improved",
      yn == "Improved"  & deg == "Medium"      ~ "Moderately Improved",
      yn == "Improved"  & deg == "Substantial" ~ "Substantially Improved",
      yn == "No Change"                        ~ "No change",
      TRUE ~ NA_character_
    ),
    chgDesire = str_to_lower(str_trim(herdMgmt_whatChanges_cantMake)),
    chgDesire = case_when(
      chgDesire %in% c("yes", "y", "1", "true") ~ "Yes",
      chgDesire%in% c("no",  "n", "0", "false") ~ "No",
      is.na(chgDesire) ~ NA_character_,
      TRUE ~ str_to_title(chgDesire)  # keeps "Don't know", etc.
    )
  )
condition_order <- c(
  "Substantially Degraded","Moderately Degraded","Slightly Degraded",
  "No change",
  "Slightly Improved","Moderately Improved","Substantially Improved"
)
chgDesire_vs_condition <- chgDesire_vs_condition %>%
  mutate(condition_comparison = factor(condition_comparison, levels = condition_order))

chgDesire_vs_condition <- chgDesire_vs_condition %>%
  filter(!is.na(condition_comparison)) %>%
  group_by(condition_comparison, chgDesire) %>%
  summarise(n = n(), .groups = "drop_last") %>%
  mutate(total = sum(n), pct = n / total) %>%
  ungroup() %>%
  arrange(condition_comparison, desc(chgDesire))

kable(chgDesire_vs_condition, n = 200)
```
--------------------------------------------------------------------------------
--------------------------------------------------------------------------------





# IV. LIVESTOCK

## 1E vs. 3A--------------------------------------------------------------------
#### Have certain types of livestock increased or decreased? By Household: vs. Did you purchase supplemental fodder last year?
#### Columns: livestock_2023_camel/livestock_2023_cow/livestock_2023_horse/livestock_2023_sheep/livestock_2023_goat/livestock_2019_camel/livestock_2019_cow/livestock_2019_horse/livestock_2019_sheep/livestock_2019_goat/lastYr_fodder
```{r, echo=FALSE}
lvstk_long <- base_LIVESTOCK %>%
  select(
    Ref,
    starts_with("livestock_")
  ) %>%
  pivot_longer(
    cols = starts_with("livestock_"),
    names_to = c("year", "species"),
    names_pattern = "livestock_(\\d{4})_(.*)",
    values_to = "count_raw"
  ) %>%
  mutate(
    year = as.integer(year),
    species = str_to_lower(species),
    # handles entries like "12", "12 hd", etc.
    count = parse_number(as.character(count_raw))
  ) %>%
  select(Ref, species, year, count)

lvstk_change <- lvstk_long %>%
  pivot_wider(
    names_from = year,
    values_from = count,
    names_prefix = "y"  
    # values_fill = 0          
  ) %>%
  mutate(
    delta = y2023 - y2019,
    change = case_when(
      is.na(y2019) & is.na(y2023) ~ NA_character_,
      is.na(y2019) & !is.na(y2023) ~ "Increase (new in 2023)",
      !is.na(y2019) & is.na(y2023) ~ "Decrease (missing in 2023)",
      delta > 0 ~ "Increase",
      delta < 0 ~ "Decrease",
      TRUE ~ "No change"
    ),
    # Optional: human-readable label like your original idea
    change_label = case_when(
      is.na(delta) ~ NA_character_,
      delta > 0 ~ paste0("2023: more ", species),
      delta < 0 ~ paste0("2023: fewer ", species),
      TRUE ~ paste0("2023: same ", species)
    )
  ) %>%
  arrange(Ref, species)

lvstk_change2 <- lvstk_change %>%
  left_join(
    base_LIVESTOCK %>% select(Ref, lastYr_fodder),
    by = "Ref"
  ) %>%
  mutate(
    lastYr_fodder = str_to_lower(str_trim(lastYr_fodder)),
    lastYr_fodder = case_when(
      lastYr_fodder %in% c("yes", "y", "1", "true") ~ "Yes",
      lastYr_fodder %in% c("no",  "n", "0", "false") ~ "No",
      is.na(lastYr_fodder) ~ NA_character_,
      TRUE ~ str_to_title(lastYr_fodder)  # keeps "Don't know", etc.
    )
  )

change_vs_fodder <- lvstk_change2 %>%
  filter(!is.na(change_label)) %>%
  count(change_label, lastYr_fodder, sort = TRUE)

change_vs_fodder_wide <- change_vs_fodder %>%
  filter(lastYr_fodder %in% c("Yes","No")) %>%
  pivot_wider(names_from = lastYr_fodder, values_from = n, values_fill = 0) %>%
  rename(
    lastYrfodder_yes = Yes,
    lastYrfodder_no  = No
  ) %>%
  mutate(
    total_ = lastYrfodder_yes + lastYrfodder_no,
    pct_yes = if_else(total_ > 0, lastYrfodder_yes / total_, NA_real_)
  ) %>%
  arrange(desc(pct_yes), desc(total_))

kable(change_vs_fodder_wide, n = 200)
```


## 1E vs. 4A--------------------------------------------------------------------
#### Have certain types of livestock increased or decreased? by Soum: vs. Do you plan to purchase supplemental fodder this year?
#### Columns: livestock_2023_camel/livestock_2023_cow/livestock_2023_horse/livestock_2023_sheep/livestock_2023_goat/livestock_2019_camel/livestock_2019_cow/livestock_2019_horse/livestock_2019_sheep/livestock_2019_goat/thisYr_fodder
```{r, echo=FALSE}
lvstk_long <- base_LIVESTOCK %>%
  select(
    Ref,
    starts_with("livestock_")
  ) %>%
  pivot_longer(
    cols = starts_with("livestock_"),
    names_to = c("year", "species"),
    names_pattern = "livestock_(\\d{4})_(.*)",
    values_to = "count_raw"
  ) %>%
  mutate(
    year = as.integer(year),
    species = str_to_lower(species),
    # handles entries like "12", "12 hd", etc.
    count = parse_number(as.character(count_raw))
  ) %>%
  select(Ref, species, year, count)

lvstk_change <- lvstk_long %>%
  pivot_wider(
    names_from = year,
    values_from = count,
    names_prefix = "y"  
    # values_fill = 0          
  ) %>%
  mutate(
    delta = y2023 - y2019,
    change = case_when(
      is.na(y2019) & is.na(y2023) ~ NA_character_,
      is.na(y2019) & !is.na(y2023) ~ "Increase (new in 2023)",
      !is.na(y2019) & is.na(y2023) ~ "Decrease (missing in 2023)",
      delta > 0 ~ "Increase",
      delta < 0 ~ "Decrease",
      TRUE ~ "No change"
    ),
    # Optional: human-readable label like your original idea
    change_label = case_when(
      is.na(delta) ~ NA_character_,
      delta > 0 ~ paste0("2023: more ", species),
      delta < 0 ~ paste0("2023: fewer ", species),
      TRUE ~ paste0("2023: same ", species)
    )
  ) %>%
  arrange(Ref, species)

lvstk_change2 <- lvstk_change %>%
  left_join(
    base_LIVESTOCK %>% select(Ref, thisYr_fodder),
    by = "Ref"
  ) %>%
  mutate(
    thisYr_fodder = str_to_lower(str_trim(thisYr_fodder)),
    thisYr_fodder = case_when(
      thisYr_fodder %in% c("yes", "y", "1", "true") ~ "Yes",
      thisYr_fodder %in% c("no",  "n", "0", "false") ~ "No",
      is.na(thisYr_fodder) ~ NA_character_,
      TRUE ~ str_to_title(thisYr_fodder)  # keeps "Don't know", etc.
    )
  )

change_vs_fodder2 <- lvstk_change2 %>%
  filter(!is.na(change_label)) %>%
  count(change_label, thisYr_fodder, sort = TRUE)

change_vs_fodder_wide2 <- change_vs_fodder2 %>%
  filter(thisYr_fodder %in% c("Yes","No")) %>%
  pivot_wider(names_from = thisYr_fodder, values_from = n, values_fill = 0) %>%
  rename(
    thisYrfodder_yes = Yes,
    thisYrfodder_no  = No
  ) %>%
  mutate(
    total_ = thisYrfodder_yes + thisYrfodder_no,
    pct_yes = if_else(total_ > 0, thisYrfodder_yes / total_, NA_real_)
  ) %>%
  arrange(desc(pct_yes), desc(total_))

kable(change_vs_fodder_wide2, n = 200)
```


## 1E vs. 4B --------------------------------------------------------------------
#### Have certain types of livestock increased or decreased? by Soum: vs. Have you noticed any long term shifts in vegetation/forage?
#### Columns: livestock_2023_camel/livestock_2023_cow/livestock_2023_horse/livestock_2023_sheep/livestock_2023_goat/livestock_2019_camel/livestock_2019_cow/livestock_2019_horse/livestock_2019_sheep/livestock_2019_goat/vegShifts_yn/vegShifts_quanQual
```{r, echo=FALSE}
lvstk_long <- base_LIVESTOCK %>%
  select(
    Ref,
    starts_with("livestock_")
  ) %>%
  pivot_longer(
    cols = starts_with("livestock_"),
    names_to = c("year", "species"),
    names_pattern = "livestock_(\\d{4})_(.*)",
    values_to = "count_raw"
  ) %>%
  mutate(
    year = as.integer(year),
    species = str_to_lower(species),
    # handles entries like "12", "12 hd", etc.
    count = parse_number(as.character(count_raw))
  ) %>%
  select(Ref, species, year, count)

lvstk_change <- lvstk_long %>%
  pivot_wider(
    names_from = year,
    values_from = count,
    names_prefix = "y"  
    # values_fill = 0          
  ) %>%
  mutate(
    delta = y2023 - y2019,
    change = case_when(
      is.na(y2019) & is.na(y2023) ~ NA_character_,
      is.na(y2019) & !is.na(y2023) ~ "Increase (new in 2023)",
      !is.na(y2019) & is.na(y2023) ~ "Decrease (missing in 2023)",
      delta > 0 ~ "Increase",
      delta < 0 ~ "Decrease",
      TRUE ~ "No change"
    ),
    # Optional: human-readable label like your original idea
    change_label = case_when(
      is.na(delta) ~ NA_character_,
      delta > 0 ~ paste0("2023: more ", species),
      delta < 0 ~ paste0("2023: fewer ", species),
      TRUE ~ paste0("2023: same ", species)
    )
  ) %>%
  arrange(Ref, species)


pastureChg1 <- base_LIVESTOCK %>% 
  select(Ref, vegShifts_yn, vegShifts_quanQual) %>%
  mutate(
    condition_comparison = case_when(
      vegShifts_yn == "Yes" & vegShifts_quanQual == "Quantity" ~ "Yes: Quantity",
      vegShifts_yn == "Yes" & vegShifts_quanQual == "Quality" ~ "Yes: Quality",
      vegShifts_yn == "Yes" & vegShifts_quanQual == "Both" ~ "Yes: Both",
      vegShifts_yn == "No" ~ "No change",
      TRUE ~ "Unclear"
    )) 


lvstk_change3 <- lvstk_change %>%
  left_join(
    pastureChg1 %>% select(Ref, condition_comparison),
    by = "Ref"
  ) %>%
  mutate(
    condition_comparison = str_to_lower(str_trim(condition_comparison)),
    condition_comparison = case_when(
      condition_comparison %in% c("yes", "y", "1", "true") ~ "Yes",
      condition_comparison %in% c("no",  "n", "0", "false") ~ "No",
      is.na(condition_comparison) ~ NA_character_,
      TRUE ~ str_to_title(condition_comparison)  # keeps "Don't know", etc.
    )
  )

change_vs_fodder4 <- lvstk_change3 %>%
  filter(!is.na(change_label)) %>%
  count(change_label, condition_comparison, sort = TRUE)

change_vs_fodder_wide3 <- change_vs_fodder4 %>%
  filter(condition_comparison %in% c("No Change","Unclear", "Yes: Both", "Yes: Quality", "Yes: Quantity")) %>%
  pivot_wider(names_from = condition_comparison, values_from = n, values_fill = 0)

kable(change_vs_fodder_wide3, n = 200)
```


## 2A vs. 3A--------------------------------------------------------------------
#### Have certain types of livestock increased or decreased? By Household: vs. Did you purchase supplemental fodder last year?
#### Columns: livestock_2023_camel/livestock_2023_cow/livestock_2023_horse/livestock_2023_sheep/livestock_2023_goat/livestock_2019_camel/livestock_2019_cow/livestock_2019_horse/livestock_2019_sheep/livestock_2019_goat/lastYr_fodder
```{r, echo=FALSE}
SFU_count <- base_LIVESTOCK %>%
  pivot_longer(
    cols = starts_with("livestock_"),
    names_to = c("year", "livestock_type"),
    names_pattern = "livestock_(\\d{4})_(.*)",
    values_to = "count_raw"
  ) %>%
  mutate(
    year = as.integer(year),
    livestock_type = str_to_lower(livestock_type),
    count = parse_number(as.character(count_raw)),
    sfu_factor = case_when(
      livestock_type == "sheep" ~ 1,
      livestock_type == "goat"  ~ 0.9,
      livestock_type == "cow"   ~ 6,
      livestock_type == "horse" ~ 7,
      livestock_type == "camel" ~ 5,
      TRUE ~ NA_real_
    ),
    sfu_total = count * sfu_factor
  ) %>%
  group_by(Ref, year) %>%
  summarise(SFU = sum(sfu_total, na.rm = TRUE), .groups = "drop") %>%
  tidyr::pivot_wider(names_from = year, values_from = SFU, names_prefix = "SFU_")

tol <- 0  
SFU_count <- SFU_count %>%
  mutate(
    delta = SFU_2023 - SFU_2019,
    SFU_comparison = case_when(
      is.na(SFU_2019) & is.na(SFU_2023) ~ NA_character_,
      is.na(SFU_2019) & !is.na(SFU_2023) ~ "2023: greater SFU",
      !is.na(SFU_2019) & is.na(SFU_2023) ~ "2023: less SFU",
      delta >  tol ~ "2023: greater SFU",
      delta < -tol ~ "2023: less SFU",
      TRUE ~ "2023: same SFU"
    )
  )

SFU_count2 <- SFU_count %>%
  left_join(base_LIVESTOCK %>% select(Ref, lastYr_fodder), by = "Ref") %>%
  mutate(
    fodder_norm = str_to_lower(str_trim(lastYr_fodder)),
    fodder_norm = case_when(
      fodder_norm %in% c("yes","y","1","true") ~ "Yes",
      fodder_norm %in% c("no","n","0","false") ~ "No",
      is.na(fodder_norm) ~ NA_character_,
      TRUE ~ str_to_title(fodder_norm)  # keeps "Don't know", etc.
    )
  )

sfu_vs_fodder <- SFU_count2 %>%
  filter(!is.na(SFU_comparison)) %>%
  count(SFU_comparison, fodder_norm, sort = TRUE)

sfu_vs_fodder_wide <- sfu_vs_fodder %>%
  filter(fodder_norm %in% c("Yes","No")) %>%
  pivot_wider(names_from = fodder_norm, values_from = n, values_fill = 0) %>%
  rename(fodder_yes = Yes, fodder_no = No) %>%
  mutate(
    total_yes_no = fodder_yes + fodder_no,
    pct_yes = if_else(total_yes_no > 0, fodder_yes / total_yes_no, NA_real_)
  ) %>%
  arrange(desc(pct_yes), desc(total_yes_no))
kable(sfu_vs_fodder_wide, n = 200)
```


## 3A vs. 4A--------------------------------------------------------------------
#### Did you purchase supplemental fodder last year? vs. 4A. Do you plan to purchase supplemental fodder this year?
#### Columns: lastYr_fodder/thisYr_fodder
```{r, echo=FALSE}
fodder_chg1 <- base_LIVESTOCK %>%
  select(Ref, lastYr_fodder, thisYr_fodder) %>% 
  mutate(
    lastYr_fodder = str_to_lower(str_trim(lastYr_fodder)),
    lastYr_fodder = case_when(
      lastYr_fodder %in% c("yes", "y", "1", "true") ~ "Yes",
      lastYr_fodder %in% c("no",  "n", "0", "false") ~ "No",
      is.na(lastYr_fodder) ~ NA_character_,
      TRUE ~ str_to_title(lastYr_fodder)
    )
  ) %>% 
  mutate(
    thisYr_fodder = str_to_lower(str_trim(thisYr_fodder)),
    thisYr_fodder = case_when(
      thisYr_fodder %in% c("yes", "y", "1", "true") ~ "Yes",
      thisYr_fodder %in% c("no",  "n", "0", "false") ~ "No",
      is.na(thisYr_fodder) ~ NA_character_,
      TRUE ~ str_to_title(thisYr_fodder)
    )
  ) 
  
fodder_chg1 <- fodder_chg1 %>%
  count(lastYr_fodder, thisYr_fodder, sort = TRUE)

kable(fodder_chg1, n = 200)
```


## 6A vs. 9A--------------------------------------------------------------------
#### Has your herd size changed over the last five years? Overall vs. Do you have plans to substantially change the size of your herd?
#### Columns: past5yrs_herdsize/nextYr_herdChg/nextYr_what
```{r, echo=FALSE}
herdSz_Chg1 <- base_LIVESTOCK %>%
  select(Ref, past5yrs_herdsize, nextYr_herdChg) %>% 
  mutate(
    past5yrs_herdsize = str_to_lower(str_trim(past5yrs_herdsize)),
    past5yrs_herdsize = case_when(
      is.na(past5yrs_herdsize) ~ NA_character_,
      TRUE ~ str_to_title(past5yrs_herdsize)
    )
  ) %>% 
  mutate(
    nextYr_herdChg = str_to_lower(str_trim(nextYr_herdChg)),
    nextYr_herdChg = case_when(
      is.na(nextYr_herdChg) ~ NA_character_,
      TRUE ~ str_to_title(nextYr_herdChg)
    )
  ) 

herdSz_Chg2 <- base_LIVESTOCK %>% 
  select(Ref, nextYr_herdChg, nextYr_what) %>%
  mutate(
    plans4Change = case_when(
      nextYr_herdChg == "Yes" & nextYr_what == "Increase" ~ "Yes: Increase",
      nextYr_herdChg == "Yes" & nextYr_what == "Quality" ~ "Yes: Decrease",
      nextYr_herdChg == "Yes" & nextYr_what == "Both" ~ "Yes: Maintain",
      nextYr_herdChg == "Yes" & nextYr_what == "Unsure" ~ "Yes: Unsure",
      nextYr_herdChg == "No" ~ "Will not change",
      TRUE ~ "Unclear"
    )) 

herdSz_Chg3 <- herdSz_Chg1 %>%
  left_join(
    herdSz_Chg2 %>% select(Ref, plans4Change),
    by = "Ref"
  ) %>%
  mutate(
    plans4Change = str_to_lower(str_trim(plans4Change)),
    plans4Change = case_when(
      is.na(plans4Change) ~ NA_character_,
      TRUE ~ str_to_title(plans4Change) 
    )
  )


herdSz_Chg4 <- herdSz_Chg3 %>%
  count(past5yrs_herdsize, plans4Change, sort = TRUE)

kable(herdSz_Chg4)
```








