---
title: "LCLUC_INTER_category_analyses"
author: "Jessie Dearing"
date: "2025-08-06"
output: pdf_document
---

This relies on the combined dfs from 1_data_import.

```{r setup , include = FALSE}
library(kableExtra)
library(ggplot2)
library(janitor)
library(skimr)
library(tidyr)
library(tidyverse)
library(dplyr)
library(purrr)
```

```{r setup, include=FALSE}
# Source the script that creates `base_`
source("1_data_import.R")  # Replace with the actual script filename

# Now `base_` should exist before calling skim()
if (exists("base_")) {
  skim(base_)
}
```

```{r, include=FALSE}

#setwd("C:/Users/jessi/OneDrive - Cornell University/Documents/MSPhD/AllingtonLab_LCLUC/RStudio_WorkingDirectory")
names(base_) <- gsub("\\.x$", "", names(base_))

str(base_)
base_ <- as.data.frame(base_)
base_ <- base_ %>% 
  mutate(across(Ref, as.factor))
```


# I. LABOR COMPARISONS

## QUESTION VS. QUESTION--------------------------------------------------------
#### How many people undertake migrations? vs. Distance for daily herding, generally
#### Columns: labor_numMigrates/herdMgmt_dailyDist
```{r, echo=FALSE}

```


## QUESTION VS. QUESTION--------------------------------------------------------
#### How many people undertake migrations? vs. Distance for daily herding, generally
#### Columns: labor_numMigrates/herdMgmt_dailyDist
```{r, echo=FALSE}

```


## QUESTION VS. QUESTION--------------------------------------------------------
#### How many people undertake migrations? vs. Distance for daily herding, generally
#### Columns: labor_numMigrates/herdMgmt_dailyDist
```{r, echo=FALSE}

```


## QUESTION VS. QUESTION--------------------------------------------------------
#### How many people undertake migrations? vs. Distance for daily herding, generally
#### Columns: labor_numMigrates/herdMgmt_dailyDist
```{r, echo=FALSE}

```


## QUESTION VS. QUESTION--------------------------------------------------------
#### How many people undertake migrations? vs. Distance for daily herding, generally
#### Columns: labor_numMigrates/herdMgmt_dailyDist
```{r, echo=FALSE}

```


## QUESTION VS. QUESTION--------------------------------------------------------
#### How many people undertake migrations? vs. Distance for daily herding, generally
#### Columns: labor_numMigrates/herdMgmt_dailyDist
```{r, echo=FALSE}

```


## QUESTION VS. QUESTION--------------------------------------------------------
#### How many people undertake migrations? vs. Distance for daily herding, generally
#### Columns: labor_numMigrates/herdMgmt_dailyDist
```{r, echo=FALSE}

```


## QUESTION VS. QUESTION--------------------------------------------------------
#### How many people undertake migrations? vs. Distance for daily herding, generally
#### Columns: labor_numMigrates/herdMgmt_dailyDist
```{r, echo=FALSE}

```


## QUESTION VS. QUESTION--------------------------------------------------------
#### How many people undertake migrations? vs. Distance for daily herding, generally
#### Columns: labor_numMigrates/herdMgmt_dailyDist
```{r, echo=FALSE}

```


## QUESTION VS. QUESTION--------------------------------------------------------
#### How many people undertake migrations? vs. Distance for daily herding, generally
#### Columns: labor_numMigrates/herdMgmt_dailyDist
```{r, echo=FALSE}

```


## QUESTION VS. QUESTION--------------------------------------------------------
#### How many people undertake migrations? vs. Distance for daily herding, generally
#### Columns: labor_numMigrates/herdMgmt_dailyDist
```{r, echo=FALSE}

```


## QUESTION VS. QUESTION--------------------------------------------------------
#### How many people undertake migrations? vs. Distance for daily herding, generally
#### Columns: labor_numMigrates/herdMgmt_dailyDist
```{r, echo=FALSE}

```


## QUESTION VS. QUESTION--------------------------------------------------------
#### How many people undertake migrations? vs. Distance for daily herding, generally
#### Columns: labor_numMigrates/herdMgmt_dailyDist
```{r, echo=FALSE}

```


## QUESTION VS. QUESTION--------------------------------------------------------
#### How many people undertake migrations? vs. Distance for daily herding, generally
#### Columns: labor_numMigrates/herdMgmt_dailyDist
```{r, echo=FALSE}

```


## QUESTION VS. QUESTION--------------------------------------------------------
#### How many people undertake migrations? vs. Distance for daily herding, generally
#### Columns: labor_numMigrates/herdMgmt_dailyDist
```{r, echo=FALSE}

```


## QUESTION VS. QUESTION--------------------------------------------------------
#### How many people undertake migrations? vs. Distance for daily herding, generally
#### Columns: labor_numMigrates/herdMgmt_dailyDist
```{r, echo=FALSE}

```


## QUESTION VS. QUESTION--------------------------------------------------------
#### How many people undertake migrations? vs. Distance for daily herding, generally
#### Columns: labor_numMigrates/herdMgmt_dailyDist
```{r, echo=FALSE}

```


## QUESTION VS. QUESTION--------------------------------------------------------
#### How many people undertake migrations? vs. Distance for daily herding, generally
#### Columns: labor_numMigrates/herdMgmt_dailyDist
```{r, echo=FALSE}

```


## QUESTION VS. QUESTION--------------------------------------------------------
#### How many people undertake migrations? vs. Distance for daily herding, generally
#### Columns: labor_numMigrates/herdMgmt_dailyDist
```{r, echo=FALSE}

```

------------------------------------------------------------------------------
--------------------------------------------------------------------------------


# II. ALTERNATIVE LIVELIHOOD COMPARISONS

## QUESTION VS. QUESTION--------------------------------------------------------
#### How many people undertake migrations? vs. Distance for daily herding, generally
#### Columns: labor_numMigrates/herdMgmt_dailyDist
```{r, echo=FALSE}

```


## QUESTION VS. QUESTION--------------------------------------------------------
#### How many people undertake migrations? vs. Distance for daily herding, generally
#### Columns: labor_numMigrates/herdMgmt_dailyDist
```{r, echo=FALSE}

```


## QUESTION VS. QUESTION--------------------------------------------------------
#### How many people undertake migrations? vs. Distance for daily herding, generally
#### Columns: labor_numMigrates/herdMgmt_dailyDist
```{r, echo=FALSE}

```


## QUESTION VS. QUESTION--------------------------------------------------------
#### How many people undertake migrations? vs. Distance for daily herding, generally
#### Columns: labor_numMigrates/herdMgmt_dailyDist
```{r, echo=FALSE}

```


## QUESTION VS. QUESTION--------------------------------------------------------
#### How many people undertake migrations? vs. Distance for daily herding, generally
#### Columns: labor_numMigrates/herdMgmt_dailyDist
```{r, echo=FALSE}

```


## QUESTION VS. QUESTION--------------------------------------------------------
#### How many people undertake migrations? vs. Distance for daily herding, generally
#### Columns: labor_numMigrates/herdMgmt_dailyDist
```{r, echo=FALSE}

```


## QUESTION VS. QUESTION--------------------------------------------------------
#### How many people undertake migrations? vs. Distance for daily herding, generally
#### Columns: labor_numMigrates/herdMgmt_dailyDist
```{r, echo=FALSE}

```

--------------------------------------------------------------------------------
--------------------------------------------------------------------------------


# II. ALTERNATIVE LIVELIHOOD COMPARISONS

## QUESTION VS. QUESTION--------------------------------------------------------
#### How many people undertake migrations? vs. Distance for daily herding, generally
#### Columns: labor_numMigrates/herdMgmt_dailyDist
```{r, echo=FALSE}

```


## QUESTION VS. QUESTION--------------------------------------------------------
#### How many people undertake migrations? vs. Distance for daily herding, generally
#### Columns: labor_numMigrates/herdMgmt_dailyDist
```{r, echo=FALSE}

```


## QUESTION VS. QUESTION--------------------------------------------------------
#### How many people undertake migrations? vs. Distance for daily herding, generally
#### Columns: labor_numMigrates/herdMgmt_dailyDist
```{r, echo=FALSE}

```


## QUESTION VS. QUESTION--------------------------------------------------------
#### How many people undertake migrations? vs. Distance for daily herding, generally
#### Columns: labor_numMigrates/herdMgmt_dailyDist
```{r, echo=FALSE}

```


## QUESTION VS. QUESTION--------------------------------------------------------
#### How many people undertake migrations? vs. Distance for daily herding, generally
#### Columns: labor_numMigrates/herdMgmt_dailyDist
```{r, echo=FALSE}

```


## QUESTION VS. QUESTION--------------------------------------------------------
#### How many people undertake migrations? vs. Distance for daily herding, generally
#### Columns: labor_numMigrates/herdMgmt_dailyDist
```{r, echo=FALSE}

```

--------------------------------------------------------------------------------
--------------------------------------------------------------------------------


