---
title: LCLUC Later Stage Analyses
author: "Jessie Dearing"
date: "2025-06-26"
output: pdf_document
---

This relies on the combined dfs from 1_data_import. There is not currently any commentary in this document because I'm still running through analyses and chunking them in here as I go. 

```{r setup , include = FALSE}
library(kableExtra)
library(ggplot2)
library(janitor)
library(skimr)
library(tidyr)
library(tidyverse)
library(dplyr)
library(purrr)
```

```{r setup, include=FALSE}
# Source the script that creates `base_`
source("1_data_import.R")  # Replace with the actual script filename

# Now `base_` should exist before calling skim()
if (exists("base_")) {
  skim(base_)
}
```

```{r, include=FALSE}

#setwd("C:/Users/jessi/OneDrive - Cornell University/Documents/MSPhD/AllingtonLab_LCLUC/RStudio_WorkingDirectory")
names(base_) <- gsub("\\.x$", "", names(base_))

str(base_)
base_ <- as.data.frame(base_)
base_ <- base_ %>% 
  mutate(across(Ref, as.factor))
```

# I. LABOR

### 1. Who does the daily moves for herding? 
  Column: (labor_whoMovesDaily) 
  (broken up by soum)
```{r, echo=FALSE}
count_dailyMoves <- base_LABOR %>%
  select(Soum, labor_whoMovesDaily) %>%
  filter(!is.na(labor_whoMovesDaily)) %>%
  separate_rows(labor_whoMovesDaily, sep = ",") %>%
  mutate(
    labor_whoMovesDaily = str_trim(labor_whoMovesDaily),
    labor_whoMovesDaily = str_to_lower(labor_whoMovesDaily),
    labor_whoMovesDaily = case_when(
      labor_whoMovesDaily == "grandparents" ~ "grandparent, unspecified",
      labor_whoMovesDaily == "child" ~ "child, unspecified",
      labor_whoMovesDaily == "sibling" ~ "sibling, unspecified",
      labor_whoMovesDaily == "grandchild" ~ "grandchild, unspecified",
      TRUE ~ labor_whoMovesDaily
    )
  ) %>%
  count(Soum, labor_whoMovesDaily, sort = TRUE)

count_wide <- count_dailyMoves %>%
  pivot_wider(
    names_from = Soum,
    values_from = n,
    values_fill = 0  
  ) %>%
  rowwise() %>%
  mutate(Total = sum(c_across(where(is.numeric)))) %>%
  ungroup()
kable(count_wide)
```


### 2. Who undertakes herding migrations?
  Column: labor_whoMigrates
```{r, echo=FALSE}
relationship_order <- c("husband", "wife", "son(s)", "daughter(s)", "child(ren), unspecified", "brother(s)", "sibling(s), unspecified", "father",
  "mother", "grandparent(s), unspecified", "grandchild(ren), unspecified", "household head", "extended family/in-laws", "friend/neighbor(s)",
  "person(s), unspecified", "hired help", "just myself", "other", "husband. 2 sons")

count_whoMigrates <- base_LABOR %>%
  select(Soum, labor_whoMigrates) %>%
  filter(!is.na(labor_whoMigrates)) %>%
  mutate(labor_whoMigrates = str_replace(labor_whoMigrates, "Husband. 2 sons", "husband, sons")
  ) %>%
  separate_rows(labor_whoMigrates, sep = ",") %>%
  mutate(
    labor_whoMigrates = str_trim(labor_whoMigrates),
    labor_whoMigrates = str_to_lower(labor_whoMigrates),
    labor_whoMigrates = case_when(
      labor_whoMigrates == "grandparents" ~ "grandparent(s), unspecified",
      labor_whoMigrates == "grandmother" ~ "grandparent(s), unspecified",
      labor_whoMigrates == "child" ~ "child(ren), unspecified",
      labor_whoMigrates == "children" ~ "child(ren), unspecified",
      labor_whoMigrates == "son" ~ "son(s)",
      labor_whoMigrates == "2 sons" ~ "son(s)",
      labor_whoMigrates == "3 sons" ~ "son(s)",
      labor_whoMigrates == "son (student)" ~ "son(s)",
      labor_whoMigrates == "son (when he is available)" ~ "son(s)",
      labor_whoMigrates == "son 2" ~ "son(s)",
      labor_whoMigrates == "olders son comes to help" ~ "son(s)",
      labor_whoMigrates == "sons" ~ "son(s)",
      labor_whoMigrates == "daughter" ~ "daughter(s)",
      labor_whoMigrates == "1 daughter" ~ "daughter(s)",
      labor_whoMigrates == "2 daughters" ~ "daughter(s)",
      labor_whoMigrates == "2 children" ~ "child(ren), unspecified",
      labor_whoMigrates == "3 children" ~ "child(ren), unspecified",
      labor_whoMigrates == "4 children" ~ "child(ren), unspecified",
      labor_whoMigrates == "7 children" ~ "child(ren), unspecified",
      labor_whoMigrates == "older brother" ~ "brother(s)",
      labor_whoMigrates == "older brothers help" ~ "brother(s)",
      labor_whoMigrates == "sibling" ~ "sibling(s), unspecified",
      labor_whoMigrates == "siblings" ~ "sibling(s), unspecified",
      labor_whoMigrates == "2 younger siblings" ~ "sibling(s), unspecified",
      labor_whoMigrates == "3 siblings-neighbors" ~ "sibling(s), unspecified",
      labor_whoMigrates == "4 younger siblings" ~ "sibling(s), unspecified",
      labor_whoMigrates == "younger sibling" ~ "sibling(s), unspecified",
      labor_whoMigrates == "younger siblings 2" ~ "sibling(s), unspecified",
      labor_whoMigrates == "grandchild" ~ "grandchild(ren), unspecified",
      labor_whoMigrates == "grandchildren" ~ "grandchild(ren), unspecified",
      labor_whoMigrates == "grandchidlren" ~ "grandchild(ren), unspecified",
      labor_whoMigrates == "1" ~ "person(s), unspecified",
      labor_whoMigrates == "2" ~ "person(s), unspecified",
      labor_whoMigrates == "3" ~ "person(s), unspecified",
      labor_whoMigrates == "4" ~ "person(s), unspecified",
      labor_whoMigrates == "4 people" ~ "person(s), unspecified",
      labor_whoMigrates == "24" ~ "person(s), unspecified",
      labor_whoMigrates == "3-feb" ~ "person(s), unspecified",
      labor_whoMigrates == "6 people" ~ "person(s), unspecified",
      labor_whoMigrates == "everyone 3" ~ "person(s), unspecified",
      labor_whoMigrates == "everyone" ~ "person(s), unspecified",
      labor_whoMigrates == "neighbors" ~ "friend/neighbor(s)",
      labor_whoMigrates == "3 neighbors" ~ "friend/neighbor(s)",
      labor_whoMigrates == "2 neighbors" ~ "friend/neighbor(s)",
      labor_whoMigrates == "4 neighbors" ~ "friend/neighbor(s)",
      labor_whoMigrates == "neighbors 4" ~ "friend/neighbor(s)",
      labor_whoMigrates == "friends" ~ "friend/neighbor(s)",
      labor_whoMigrates == "daughter-in-law" ~ "extended family/in-laws",
      labor_whoMigrates == "son-in-law" ~ "extended family/in-laws",
      labor_whoMigrates == "father-in-law" ~ "extended family/in-laws",
      labor_whoMigrates == "brother-in-law" ~ "extended family/in-laws",
      labor_whoMigrates == "extended family members" ~ "extended family/in-laws",
      labor_whoMigrates == "herder children's families" ~ "extended family/in-laws",
      labor_whoMigrates == "in soum" ~ "extended family/in-laws",
      labor_whoMigrates == "school children" ~ "extended family/in-laws",
      labor_whoMigrates == "wide" ~ "extended family/in-laws",
      labor_whoMigrates == "younger brother and his wife" ~ "extended family/in-laws",
      labor_whoMigrates == "extended families" ~ "extended family/in-laws",
      labor_whoMigrates == "assistant herder" ~ "hired help",
      labor_whoMigrates == "herders 4" ~ "hired help",
      labor_whoMigrates == "50 year old" ~ "other",
      labor_whoMigrates == "ask for help" ~ "other",
      labor_whoMigrates == "ask someone for help" ~ "other",
      labor_whoMigrates == "don't move" ~ "other",
      labor_whoMigrates == "me" ~ "just myself",
      labor_whoMigrates == "0" ~ "just myself",
      labor_whoMigrates == "others" ~ "other",
      TRUE ~ labor_whoMigrates
    )
  ) %>%
  count(Soum, labor_whoMigrates, sort = FALSE) %>%
  mutate(labor_whoMigrates = factor(labor_whoMigrates, levels = relationship_order)) %>%
  arrange(labor_whoMigrates)

count_wide2 <- count_whoMigrates %>%
  pivot_wider(
    names_from = Soum,
    values_from = n,
    values_fill = 0  
  ) %>%
  rowwise() %>%
  mutate(Total = sum(c_across(-1))) %>%  
  ungroup()

kable(count_wide2)
```


### 3. How many people undertake migrations?
  Column: labor_numMigrates
```{r, echo=FALSE}
count_numMigrates <- base_LABOR %>%
  select(Soum, labor_numMigrates) %>%
  filter(!is.na(labor_numMigrates)) %>%
  count(Soum, labor_numMigrates, sort = TRUE)

count_wide3 <- count_numMigrates %>%
  pivot_wider(
    names_from = Soum,
    values_from = n,
    values_fill = 0
  ) %>%
  rowwise() %>%
  mutate(Total = sum(c_across(-1))) %>% 
  ungroup()

kable(count_wide3)
```


### 4.  Does migration impact labor and/or herding practices?
#### A. Impact on labor: 
  Column: labor_migImpactLabor
```{r, echo=FALSE}
count_migImpactLabor <- base_LABOR %>%
  select(Soum, labor_migImpactLabor) %>%
  count(Soum, labor_migImpactLabor, sort = TRUE)
count_wide4 <- count_migImpactLabor %>%
  pivot_wider(
    names_from = Soum,
    values_from = n,
    values_fill = 0 
  ) %>%
  rowwise() %>%
  mutate(Total = sum(c_across(where(is.numeric)))) %>%
  ungroup()
kable(count_wide4)
```

#### B. Impact on herding practices:  
  Column: labor_migImpactPract
```{r, echo=FALSE}
count_migImpactPract <- base_LABOR %>%
  select(Soum, labor_migImpactPract) %>%
  count(Soum, labor_migImpactPract, sort = TRUE)
count_wide5 <- count_migImpactPract %>%
  pivot_wider(
    names_from = Soum,
    values_from = n,
    values_fill = 0
  ) %>%
  rowwise() %>%
  mutate(Total = sum(c_across(where(is.numeric)))) %>%
  ungroup()

kable(count_wide5, n = 30)
```


### 5. Do you hire labor?  
  Column: labor_hire
```{r, echo=FALSE}
count_hireYN <- base_LABOR %>%
  select(Soum, labor_hire) %>%
  count(Soum, labor_hire, sort = TRUE)
count_wide6 <- count_hireYN %>%
  pivot_wider(
    names_from = Soum,
    values_from = n,
    values_fill = 0 
  ) %>%
  rowwise() %>%
  mutate(Total = sum(c_across(where(is.numeric)))) %>%
  ungroup()
kable(count_wide6)
```


### 6. If you do hire labor, for what?
#### A. Moving the herds daily:
  Column: labor_hire_DailyMove
```{r, echo=FALSE}
count_hire_dailyMove <- base_LABOR %>%
  select(Soum, labor_hire_dailyMove) %>%
  count(Soum, labor_hire_dailyMove, sort = TRUE)
count_wide7 <- count_hire_dailyMove %>%
  pivot_wider(
    names_from = Soum,
    values_from = n,
    values_fill = 0  
  ) %>%
  rowwise() %>%
  mutate(Total = sum(c_across(where(is.numeric)))) %>%
  ungroup()
kable(count_wide7)
```

#### B. Moving the herds seasonally:
  Column: labor_hire_bigMove
```{r, echo=FALSE}
count_hire_bigMove <- base_LABOR %>%
  select(Soum, labor_hire_bigMove) %>%
  count(Soum, labor_hire_bigMove, sort = TRUE)
count_wide8 <- count_hire_bigMove %>%
  pivot_wider(
    names_from = Soum,
    values_from = n,
    values_fill = 0  
  ) %>%
  rowwise() %>%
  mutate(Total = sum(c_across(where(is.numeric)))) %>%
  ungroup()
kable(count_wide8)
```

#### C. Moving the herds for Otor: 
  Column: labor_hire_forOtor
```{r, echo=FALSE}
count_hire_Otor <- base_LABOR %>%
  select(Soum, labor_hire_forOtor) %>%
  count(Soum, labor_hire_forOtor, sort = TRUE)
count_wide9 <- count_hire_Otor %>%
  pivot_wider(
    names_from = Soum,
    values_from = n,
    values_fill = 0
  ) %>%
  rowwise() %>%
  mutate(Total = sum(c_across(where(is.numeric)))) %>%
  ungroup()
kable(count_wide9)
```

#### D. Hiring for other tasks: 
  Column: labor_hire_Other
```{r, echo=FALSE}
count_hire_OTHER <- base_LABOR %>%
  select(Soum, labor_hire_Other) %>%
  separate_rows(labor_hire_Other, sep = ",") %>%
  mutate(
    labor_hire_Other = str_trim(labor_hire_Other),
    labor_hire_Other = str_to_lower(labor_hire_Other)
    ) %>% 
  count(Soum, labor_hire_Other, sort = TRUE)
count_wide10 <- count_hire_OTHER %>%
  pivot_wider(
    names_from = Soum,
    values_from = n,
    values_fill = 0
  ) %>%
  rowwise() %>%
  mutate(Total = sum(c_across(where(is.numeric)))) %>%
  ungroup()
kable(count_wide10)
```

--------------------------------------------------------------------------------






# II. TENURE

### 1. Land tenure arrangements: 
#### A. Cross-tab:
  Not the best looking, I'll work on making it more legible. Is easier to look at if it's viewed in the markdown or in the script. 
```{r, echo=FALSE}
cross_tab <- base_TENURE %>%
  mutate(wintCamp = replace_na(wintCamp, "No"),
         wintContract = replace_na(wintContract, "No"),
         wintPas = replace_na(wintCamp, "No"),
         wintPasContract = replace_na(wintPasContract, "No"),
         sameCamp = replace_na(sameCamp, "No"),
         sprCamp = replace_na(sprCamp, "No"),
         sprCampContract = replace_na(sprCampContract, "No"),
         sprPasContract = replace_na(sprPasContract, "No"),
         )

cross_tab <- xtabs(~ wintCamp + 
                     wintContract + 
                     wintPas + 
                     wintPasContract + 
                     sameCamp + 
                     sprCamp + 
                     sprCampContract + 
                     sprPasContract, 
                   data = base_TENURE)
ftable(cross_tab)
```

#### B. Contingency table:
  This one looks better and is depicting the same information.
```{r, echo=FALSE}
base_contingency <- base_TENURE %>%
  mutate(wintCamp = replace_na(wintCamp, "No"),
         wintContract = replace_na(wintContract, "No"),
         wintPas = replace_na(wintPas, "No"),
         wintPasContract = replace_na(wintPasContract, "No"),
         sameCamp = replace_na(sameCamp, "No"),
         sprCamp = replace_na(sprCamp, "No"),
         sprCampContract = replace_na(sprCampContract, "No"),
         sprPasContract = replace_na(sprPasContract, "No"),
         )

contingency_table <- base_contingency %>%
  count(wintCamp, 
        wintContract, 
        wintPas, 
        wintPasContract, 
        sameCamp, 
        sprCamp, 
        sprCampContract, 
        sprPasContract, 
        sort = TRUE
        )
kable(contingency_table)
```


### 2. Contingency Tables on tenure, by Soum: 
#### A. Winter Camp (y/n): 
```{r, echo=FALSE}
tenure_table_wintCamp <- table(base_contingency$Soum, base_contingency$wintCamp)
kable(tenure_table_wintCamp)
```

#### B. Winter Camp Contract (y/n): 
```{r, echo=FALSE}
tenure_table_wintContract <- table(base_contingency$Soum, base_contingency$wintContract)
kable(tenure_table_wintContract)
```

#### C. Winter Pasture (y/n):
```{r, echo=FALSE}
tenure_table_wintPas <- table(base_contingency$Soum, base_contingency$wintPas)
kable(tenure_table_wintPas)
```

#### D. Winter Paster Contract (y/n): 
```{r, echo=FALSE}
tenure_table_wintPasContract <- table(base_contingency$Soum, base_contingency$wintPasContract)
kable(tenure_table_wintPasContract)
```

#### E. Is your winter camp your spring camp (y/n)?  
```{r, echo=FALSE}
tenure_table_sameCamp <- table(base_contingency$Soum, base_contingency$sameCamp)
kable(tenure_table_sameCamp)
```

#### F. Spring Camp? (y/n):   
```{r, echo=FALSE}
tenure_table_sprCamp <- table(base_contingency$Soum, base_contingency$sprCamp)
kable(tenure_table_sprCamp)
```

#### G. Spring Camp Contract (y/n):
```{r, echo=FALSE}
tenure_table_sprCampContract <- table(base_contingency$Soum, base_contingency$sprCampContract)
kable(tenure_table_sprCampContract)
```

#### H. Spring Pasture Contract (y/n): 
```{r, echo=FALSE}
tenure_table_sprPasContract <- table(base_contingency$Soum, base_contingency$sprPasContract)
kable(tenure_table_sprPasContract)
```
--------------------------------------------------------------------------------






# III. ALTERNATIVE LIVELIHOODS


### 1. Is someone in the household doing non-herding work?
  Column: altLife_nonHerdWork
```{r, echo=FALSE}
altLife_table_nonHerdWork <- table(base_ALTLIFE$Soum, base_ALTLIFE$altLife_nonHerdWork)
print(altLife_table_nonHerdWork)
```
#### A. If so, who is doing the non-herding work?   
  Column: labor_hire
```{r, echo=FALSE}
count_whoNoHerdWork <- base_ALTLIFE %>%
  select(Soum, altLife_whoNoHerdwork) %>%
  filter(!is.na(altLife_whoNoHerdwork)) %>%
  separate_rows(altLife_whoNoHerdwork, sep = ",") %>%
  mutate(
    altLife_whoNoHerdwork = str_trim(altLife_whoNoHerdwork),
    altLife_whoNoHerdwork = str_to_lower(altLife_whoNoHerdwork),
    altLife_whoNoHerdwork = case_when(
      altLife_whoNoHerdwork == "son-in-law" ~ "extended family members",
      altLife_whoNoHerdwork == "doctor" ~ "not specified",
      TRUE ~ altLife_whoNoHerdwork
    )
  ) %>% 
  count(Soum, altLife_whoNoHerdwork, sort = TRUE)

count_whoNoHerdWork <- count_whoNoHerdWork %>%
  pivot_wider(
    names_from = Soum,
    values_from = n,
    values_fill = 0
  ) %>%
  rowwise() %>%
  mutate(Total = sum(c_across(where(is.numeric)))) %>%
  ungroup()
kable(count_whoNoHerdWork)
```

#### B. Is so, what is the non-herding work?  
  Column: labor_hire
```{r, echo=FALSE}
count_noHerdWhatWork <- base_ALTLIFE %>%
  select(Soum, altLife_noHerdWhatWork) %>%
  filter(!is.na(altLife_noHerdWhatWork)) %>%
  separate_rows(altLife_noHerdWhatWork, sep = ",") %>%
  mutate(
    altLife_noHerdWhatWork = str_trim(altLife_noHerdWhatWork),
    altLife_noHerdWhatWork = str_to_lower(altLife_noHerdWhatWork),
    altLife_noHerdWhatWork = case_when(
      altLife_noHerdWhatWork == "bagh governor" ~ "government leadership",
      altLife_noHerdWhatWork == "public service" ~ "government employment",
      altLife_noHerdWhatWork == "employment at soum governor office" ~ "government employment",
      altLife_noHerdWhatWork == "public servant" ~ "government employment",
      altLife_noHerdWhatWork == "soum culture center" ~ "government employment",
      altLife_noHerdWhatWork == "dance instructor at culture center" ~ "government employment",
      altLife_noHerdWhatWork == "soum center" ~ "government employment",
      altLife_noHerdWhatWork == "procurement at the governor office" ~ "government employment",
      altLife_noHerdWhatWork == "social worker in ulaanbaatar hospital" ~ "government employment",
      altLife_noHerdWhatWork == "employment in environmental agency" ~ "government employment",
      altLife_noHerdWhatWork == "mining" ~ "mining and construction",
      altLife_noHerdWhatWork == "employment in mining" ~ "mining and construction",
      altLife_noHerdWhatWork == "part-time employment in mining" ~ "mining and construction",
      altLife_noHerdWhatWork == "drives truck in mining" ~ "mining and construction",
      altLife_noHerdWhatWork == "employment in construction" ~ "mining and construction",
      altLife_noHerdWhatWork == "metal work (sometimes)" ~ "mining and construction",
      altLife_noHerdWhatWork == "plumber" ~ "mining and construction",
      altLife_noHerdWhatWork == "driver" ~ "mining and construction",
      altLife_noHerdWhatWork == "employment in restaurant" ~ "commerce-related and restaurants",
      altLife_noHerdWhatWork == "cook at school kitchen" ~ "commerce-related and restaurants",
      altLife_noHerdWhatWork == "retail business" ~ "commerce-related and restaurants",
      altLife_noHerdWhatWork == "cook at kindergarten" ~ "commerce-related and restaurants",
      altLife_noHerdWhatWork == "cashier at grocery store" ~ "commerce-related and restaurants",
      altLife_noHerdWhatWork == "part-time cashier at supermarket" ~ "commerce-related and restaurants",
      altLife_noHerdWhatWork == "any part-time job" ~ "commerce-related and restaurants",
      altLife_noHerdWhatWork == "running store" ~ "commerce-related and restaurants",
      altLife_noHerdWhatWork == "working at supermarket" ~ "commerce-related and restaurants",
      altLife_noHerdWhatWork == "commercial service" ~ "commerce-related and restaurants",
      altLife_noHerdWhatWork == "work at supermarket" ~ "commerce-related and restaurants",
      altLife_noHerdWhatWork == "private business" ~ "commerce-related and restaurants",
      altLife_noHerdWhatWork == "kindergarten teacher" ~ "education",
      altLife_noHerdWhatWork == "school teacher" ~ "education",
      altLife_noHerdWhatWork == "driving instructor" ~ "education",
      altLife_noHerdWhatWork == "assistant teacher at kindergarten" ~ "education",
      altLife_noHerdWhatWork == "studies in japan" ~ "education",
      altLife_noHerdWhatWork == "teacher at kindergarten" ~ "education",
      altLife_noHerdWhatWork == "subsidy for wool/hide" ~ "agriculture and pastoralist-adjacent",
      altLife_noHerdWhatWork == "working the hide" ~ "agriculture and pastoralist-adjacent",
      altLife_noHerdWhatWork == "crop farming" ~ "agriculture and pastoralist-adjacent",
      altLife_noHerdWhatWork == "dairy store" ~ "agriculture and pastoralist-adjacent",
      altLife_noHerdWhatWork == "sales from dairy products" ~ "agriculture and pastoralist-adjacent",
      altLife_noHerdWhatWork == "employment" ~ "employment unspecified",
      altLife_noHerdWhatWork == "in ulaanbaatar" ~ "employment unspecified",
      altLife_noHerdWhatWork == "pension" ~ "employment unspecified",
      altLife_noHerdWhatWork == "salary" ~ "employment unspecified",
      altLife_noHerdWhatWork == "grandmother" ~ "employment unspecified",
      altLife_noHerdWhatWork == "employed" ~ "employment unspecified",
      altLife_noHerdWhatWork == "knitting" ~ "arts, crafts, and handwork",
      altLife_noHerdWhatWork == "horse archery" ~ "arts, crafts, and handwork",
      altLife_noHerdWhatWork == "film director" ~ "arts, crafts, and handwork",
      altLife_noHerdWhatWork == "tailoring" ~ "arts, crafts, and handwork",
      altLife_noHerdWhatWork == "doctor" ~ "medical/veterinary",
      altLife_noHerdWhatWork == "veterinarian" ~ "medical/veterinary",
      altLife_noHerdWhatWork == "cleaner" ~ "mischellaneous",
      altLife_noHerdWhatWork == "head of the soum disabled community" ~ "mischellaneous",
      altLife_noHerdWhatWork == "security" ~ "mischellaneous",
      TRUE ~ altLife_noHerdWhatWork
    )
  ) %>% 
  count(Soum, altLife_noHerdWhatWork, sort = TRUE)

count_noHerdWhatWork <- count_noHerdWhatWork %>%
  pivot_wider(
    names_from = Soum,
    values_from = n,
    values_fill = 0
  ) %>%
  rowwise() %>%
  mutate(Total = sum(c_across(where(is.numeric)))) %>%
  ungroup()
kable(count_noHerdWhatWork)
```


### 2. Additional sources of income for the household? Broken up by Soum
  Column: altLife_otherInc
```{r, echo=FALSE}
count_otherInc <- base_ALTLIFE %>%
  select(Soum, altLife_otherInc) %>%
  filter(!is.na(altLife_otherInc)) %>%
  separate_rows(altLife_otherInc, sep = ",") %>%
  mutate(
    altLife_otherInc = str_trim(altLife_otherInc),
    altLife_otherInc = str_to_lower(altLife_otherInc),
    altLife_otherInc = case_when(
      altLife_otherInc == "bagh governor" ~ "government leadership",
      TRUE ~ altLife_otherInc
    )
  ) %>% 
  count(Soum, altLife_otherInc, sort = TRUE)

count_otherInc <- count_otherInc %>%
  pivot_wider(
    names_from = Soum,
    values_from = n,
    values_fill = 0  # Fill missing values with 0s
  ) %>%
  rowwise() %>%
  mutate(Total = sum(c_across(where(is.numeric)))) %>%
  ungroup()
kable(count_otherInc)
```


### 3. Loans:
#### A. Number of loans taken out per year?
  Column: altLife_loansPerYr
```{r, echo=FALSE}
altLife_table_loansPerYr <- table(base_ALTLIFE$Soum, base_ALTLIFE$altLife_loansPerYr)
kable(altLife_table_loansPerYr)
```

#### B. Loan Sizes (min, max, mean, median, range)  
  Column: altLife_loansMin/altLife_loansMax
```{r, echo=FALSE}
base_loans <- base_ALTLIFE %>%
  select(Soum, altLife_loansMin, altLife_loansMax) %>%
  group_by(Soum) %>%  # Group by Soum before summarizing
  summarise(
    min_minLn = min(altLife_loansMin, na.rm = TRUE),
    max_minLn = max(altLife_loansMin, na.rm = TRUE),
    mean_minLn = mean(altLife_loansMin, na.rm = TRUE),
    median_minLn = median(altLife_loansMin, na.rm = TRUE),
    min_maxLn = min(altLife_loansMax, na.rm = TRUE),
    max_maxLn = max(altLife_loansMax, na.rm = TRUE),
    mean_maxLn = mean(altLife_loansMax, na.rm = TRUE),
    median_maxLn = median(altLife_loansMax, na.rm = TRUE)
    )
kable(base_loans)
```

#### C. When do you typically need loans?  
  Column: altLife_loansWhenNeed
```{r, echo=FALSE}
count_loansWhenNeed <- base_ALTLIFE %>%
  select(Soum, altLife_loansWhenNeed) %>%
  filter(!is.na(altLife_loansWhenNeed)) %>%
  mutate(
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "Winter and spring", "winter, spring"),
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "Winter and Spring", "winter, spring"),
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "august- for school year and lunar new year", "autumn, lunar new year"),
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "Winter-fodder", "winter"),
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "winter-fodder", "winter"),
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "Winter- require fodder", "winter"),
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "and Winter", "winter"),
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "winter and petrol", "winter"),
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "february", "winter"),
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "February", "winter"),
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "After December", "winter"),
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "Winter and preparation of fodder", "winter"),
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "Dec", "winter"),
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "december", "winter"),
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "winter-winter for fodder", "winter"),
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "winterember", "winter"),
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "Winter Nov-March", "winter"),
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "winter and spring", "winter, spring"),
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "winter and Lunar new year", "winter, lunar new year"),
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "Winter and Lunar new year", "winter, lunar new year"),
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "Winter and Lunar New Year", "winter, lunar new year"),
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "spring and autumn", "spring, autumn"),
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "spring-fodder", "spring"),
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "Spring- before cashmere collection", "spring"),
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "Lunar new year-spring", "spring, lunar new year"),
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "summer and winter", "summer, winter"),
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "Sep-fodder", "autumn"),
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "autumn-fodder", "autumn"),
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "prepare fodder in Autumn", "autumn"),
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "August", "autumn"),
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "Autumn- school year", "autumn"),
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "Autumn- school new year", "autumn"),
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "Aug", "autumn"),
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "autumn-sep", "autumn"),
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "Autumn-sep", "autumn"),
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "October", "autumn"),
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "September", "autumn"),
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "Autumn- student tuition fee payment and buying fodder", "autumn"),
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "Autumn- school year starts", "autumn"),
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "september-school year", "autumn"),
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "Autumn-school new year", "autumn"),
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "Autumn-school year starts", "autumn"),
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "autumn -sep", "autumn"),
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "autumn- for school year and lunar new year", "autumn, lunar new year"),
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "Autumn and Lunar New Year", "autumn, lunar new year"),
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "autumn and during lunar new year", "autumn, lunar new year"),
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "Lunar New Year and Sept", "autumn, lunar new year"),
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "autumn and spring-lunar new year", "autumn, lunar new year, spring"),
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "Autum and winter", "autumn, winter"),
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "september and during harsh winter", "autumn, winter"),
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "autumn and winter", "autumn, winter"),
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "Lunar New year and need of fodder", "lunar new year"), 
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "If livestock is weak", "depends on needs"), 
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "depends on demands", "depends on needs"), 
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "0", "never"), 
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "None", "never"), 
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "one", "never"),
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "nnever", "never"),
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "During migration and need of fodder", "during migration, depends on needs"), 
    altLife_loansWhenNeed = str_replace(altLife_loansWhenNeed, "Autumn and during medical treatment", "autumn, during medical treatment")
  ) %>%
  separate_rows(altLife_loansWhenNeed, sep = ",") %>%
  mutate(
    altLife_loansWhenNeed = str_trim(altLife_loansWhenNeed),
    altLife_loansWhenNeed = str_to_lower(altLife_loansWhenNeed)
  ) %>% 
  count(Soum, altLife_loansWhenNeed, sort = TRUE)

count_loansWhenNeed <- count_loansWhenNeed %>%
  pivot_wider(
    names_from = Soum,
    values_from = n,
    values_fill = 0
  ) %>%
  rowwise() %>%
  mutate(Total = sum(c_across(where(is.numeric)))) %>%
  ungroup()

kable(count_loansWhenNeed, n = 60)
```




















# IV. HERD MANAGEMENT

### 1. Distance for daily herding, generally:
  Column: altLife_nonHerdWork
#### A. All together: 
```{r, echo=FALSE}
count_DailyDist <- base_HERDMGMT %>%
  select(herdMgmt_dailyDist) %>%
  filter(!is.na(herdMgmt_dailyDist)) %>%
  count(herdMgmt_dailyDist, sort = TRUE)
kable(count_DailyDist)
```

#### B. Broken up by Soum: 
```{r, echo=FALSE}
count_DailyDist <- base_HERDMGMT %>%
  select(Soum, herdMgmt_dailyDist) %>%
  filter(!is.na(herdMgmt_dailyDist)) %>%
  count(Soum, herdMgmt_dailyDist, sort = TRUE)
count_dist1 <- count_DailyDist %>%
  pivot_wider(names_from = Soum, values_from = n, values_fill = 0) %>%
  rowwise() %>%
  ungroup()
kable(count_dist1)
```


### 2. Distances for daily herding, summer & winter: 
  Column: herdMgmt_sumDailyDist/herdMgmt_wintDailyDist
  
#### A. Basic distances, summer: 
```{r, echo=FALSE}
count_sumDailyDist <- base_HERDMGMT %>%
  select(herdMgmt_sumDailyDist) %>%
  filter(!is.na(herdMgmt_sumDailyDist)) %>%
  count(herdMgmt_sumDailyDist, sort = TRUE)
kable(count_sumDailyDist)
```

#### B. Basic distances, winter: 
```{r, echo=FALSE}
count_wintDailyDist <- base_HERDMGMT %>%
  select(herdMgmt_wintDailyDist) %>%
  filter(!is.na(herdMgmt_wintDailyDist)) %>%
  count(herdMgmt_wintDailyDist, sort = TRUE)
kable(count_wintDailyDist)
```

#### C. Basic distances, summer, by soum: 
```{r, echo=FALSE}
count_sumDailyDist2 <- base_HERDMGMT %>%
  select(Soum, herdMgmt_sumDailyDist) %>%
  filter(!is.na(herdMgmt_sumDailyDist)) %>%
  count(Soum, herdMgmt_sumDailyDist, sort = TRUE)
count_dist2 <- count_sumDailyDist2 %>%
  pivot_wider(names_from = Soum, values_from = n, values_fill = 0) %>%
  rowwise() %>%
  ungroup()
kable(count_dist2)
```

#### D. Basic distances, winter, by soum: 
```{r, echo=FALSE}
count_wintDailyDist2 <- base_HERDMGMT %>%
  select(Soum, herdMgmt_wintDailyDist) %>%
  filter(!is.na(herdMgmt_wintDailyDist)) %>%
  count(Soum, herdMgmt_wintDailyDist, sort = TRUE)
print(count_wintDailyDist2)
count_dist3 <- count_wintDailyDist2 %>%
  pivot_wider(names_from = Soum, values_from = n, values_fill = 0) %>%
  rowwise() %>%
  ungroup()
kable(count_dist3)
```



### 3. Do people travel greater distances for summer vs. winter?
 Column: herdMgmt_sumDailyDist/herdMgmt_wintDailyDist
 
#### A. All together: 
```{r, echo=FALSE}
count_distComparison <- base_HERDMGMT %>%
  mutate(
    dist_comparison = case_when(
      herdMgmt_sumDailyDist > herdMgmt_wintDailyDist ~ "greater dist in summer",
      herdMgmt_sumDailyDist < herdMgmt_wintDailyDist ~ "greater dist in winter",
      herdMgmt_sumDailyDist == herdMgmt_wintDailyDist ~ "Equal"
    )
  ) %>%
  count(dist_comparison)
kable(count_distComparison)
```

#### B. Broken up by Soum: 
```{r, echo=FALSE}
count_distComparison2 <- base_HERDMGMT %>%
  mutate(
    dist_comparison = case_when(
      herdMgmt_sumDailyDist > herdMgmt_wintDailyDist ~ "greater dist in summer",
      herdMgmt_sumDailyDist < herdMgmt_wintDailyDist ~ "greater dist in winter",
      herdMgmt_sumDailyDist == herdMgmt_wintDailyDist ~ "Equal"
    )
  ) %>%
  group_by(Soum, dist_comparison) %>%
  summarise(count = n(), .groups = "drop")
count_dist4 <- count_distComparison2 %>%
  pivot_wider(names_from = Soum, values_from = count, values_fill = 0)
kable(count_dist4)
```


### 4. Distance moved this year vs. last year: 
  Column: herdMgmt_timesMoved_thisYr/herdMgmt_timesMoved_lastYr
  
#### A. Times moved this year, broken up by Soum: 
```{r, echo=FALSE}
count_moves_thisYr <- base_HERDMGMT %>%
  select(Soum, herdMgmt_timesMoved_thisYr) %>%
  filter(!is.na(herdMgmt_timesMoved_thisYr)) %>%
  count(Soum, herdMgmt_timesMoved_thisYr, sort = TRUE)
count_moves1 <- count_moves_thisYr %>%
  pivot_wider(names_from = Soum, values_from = n, values_fill = 0) %>%
  rowwise() %>%
  ungroup()
kable(count_moves1)
```

#### B.Times moved last year, broken up by Soum: 
```{r, echo=FALSE}
count_moves_lastYr <- base_HERDMGMT %>%
  select(Soum, herdMgmt_timesMoved_lastYr) %>%
  filter(!is.na(herdMgmt_timesMoved_lastYr)) %>%
  count(Soum, herdMgmt_timesMoved_lastYr, sort = TRUE)
count_moves2 <- count_moves_lastYr %>%
  pivot_wider(names_from = Soum, values_from = n, values_fill = 0) %>%
  rowwise() %>%
  ungroup()
kable(count_moves2)

```

#### C. Times moved, this yr vs. last year, difference for everyone: 
```{r, echo=FALSE}
count_moves <- base_HERDMGMT %>%
  mutate(
    dist_comparison = case_when(
      herdMgmt_timesMoved_thisYr > herdMgmt_timesMoved_lastYr ~ "moved more this year",
      herdMgmt_timesMoved_lastYr > herdMgmt_timesMoved_thisYr ~ "moved more last year",
      herdMgmt_timesMoved_lastYr == herdMgmt_timesMoved_thisYr ~ "Equal"
    )
  ) %>%
  group_by(Soum, dist_comparison) %>%
  summarise(count = n(), .groups = "drop")
count_moves <- count_moves %>%
  pivot_wider(names_from = Soum, values_from = count, values_fill = 0)
kable(count_moves)
```

#### D. One table showing the difference, coalesced together: 
```{r, echo=FALSE}
herd_moves <- base_HERDMGMT %>%
  mutate(
    move_diff = herdMgmt_timesMoved_thisYr - herdMgmt_timesMoved_lastYr,
    move_description = case_when(
      move_diff > 0 ~ paste("moved", move_diff, "times more this year than last year"),
      move_diff < 0 ~ paste("moved", abs(move_diff), "times fewer this year than last year"),
      move_diff == 0 ~ "moved an equal number of times"
    )
  ) %>%
  select(herdMgmt_timesMoved_lastYr, herdMgmt_timesMoved_thisYr, move_diff, move_description)
move_summary <- herd_moves %>%
  count(move_description)
kable(move_summary)
```

#### E.The differences in times moved, broken up by Soum: 
1. Bayan
```{r, echo=FALSE}
herd_moves <- base_HERDMGMT %>%
  select(Soum, herdMgmt_timesMoved_lastYr, herdMgmt_timesMoved_thisYr) %>%
  mutate(
    move_diff = herdMgmt_timesMoved_thisYr - herdMgmt_timesMoved_lastYr,
    move_description = case_when(
      move_diff > 0 ~ paste("moved", move_diff, "times more this year than last year"),
      move_diff < 0 ~ paste("moved", abs(move_diff), "times fewer this year than last year"),
      move_diff == 0 ~ "moved an equal number of times"
    ))
herd_moves_bayan <- herd_moves %>%
  filter(Soum == "Bayan")
move_summary_bayan <- herd_moves_bayan %>%
  count(move_description)
kable(move_summary_bayan)
```

2. Bayantal
```{r, echo=FALSE}
herd_moves_bayantal <- herd_moves %>%
  filter(Soum == "Bayantal")
move_summary_bayantal <- herd_moves_bayantal %>%
  count(move_description)
kable(move_summary_bayantal)
```

3. Bayansagaan
```{r, echo=FALSE}
herd_moves_bayantsagaan <- herd_moves %>%
  filter(Soum == "Bayantsagaan")
move_summary_bayantsagaan <- herd_moves_bayantsagaan %>%
  count(move_description)
kable(move_summary_bayantsagaan)
```

4. Buren
```{r, echo=FALSE}
herd_moves_buren <- herd_moves %>%
  filter(Soum == "Buren")
move_summary_buren <- herd_moves_buren %>%
  count(move_description)
kable(move_summary_buren)
```

5. Delgerkhaan
```{r, echo=FALSE}
herd_moves_delgerkhaan <- herd_moves %>%
  filter(Soum == "Delgerkhaan")
move_summary_delgerkhaan <- herd_moves_delgerkhaan %>%
  count(move_description)
kable(move_summary_delgerkhaan)
```

6. Deren
```{r, echo=FALSE}
herd_moves_deren <- herd_moves %>%
  filter(Soum == "Deren")
move_summary_deren <- herd_moves_deren %>%
  count(move_description)
kable(move_summary_deren)
```

7. Erdenedalai
```{r, echo=FALSE}
herd_moves_erdenedalai <- herd_moves %>%
  filter(Soum == "Erdenedalai")
move_summary_erdenedalai <- herd_moves_erdenedalai %>%
  count(move_description)
kable(move_summary_erdenedalai)
```

8. Sumber
```{r, echo=FALSE}
herd_moves_sumber <- herd_moves %>%
  filter(Soum == "Sumber")
move_summary_sumber <- herd_moves_sumber %>%
  count(move_description)
kable(move_summary_sumber)
```




### 5. What is the average distance of moves, now vs. 10yrs ago?
  Column: herdMgmt_avgDistMoves/herdMgmt_10yrs_avgMoveDist
  
#### A. Unsimplified:
```{r, echo=FALSE}
herd_move_dif <- base_HERDMGMT %>%
  mutate(
    move_diff = herdMgmt_10yrs_avgMoveDist - herdMgmt_avgDistMoves,
    move_description = case_when(
      move_diff > 0 ~ paste("moved", move_diff, "kilometers more 10yrs ago than last year"),
      move_diff < 0 ~ paste("moved", abs(move_diff), "kilometers less 10yrs ago than last year"),
      move_diff == 0 ~ "moved an equal amount of distance"
    )
  ) %>%
  select(herdMgmt_timesMoved_lastYr, herdMgmt_timesMoved_thisYr, move_diff, move_description)
move_summary <- herd_move_dif %>%
  count(move_description) %>% 
  arrange(desc(n))
kable(move_summary)
```

#### B. Simplified:
```{r, echo=FALSE}
herd_move_difSimp <- base_HERDMGMT %>%
  mutate(
    move_diff = herdMgmt_10yrs_avgMoveDist - herdMgmt_avgDistMoves,
    move_description = case_when(
      move_diff > 0 ~ paste("moved more 10yrs ago than last year"),
      move_diff < 0 ~ paste("moved less 10yrs ago than last year"),
      move_diff == 0 ~ "moved an equal amount of distance"
    )
  ) %>%
  select(herdMgmt_timesMoved_lastYr, herdMgmt_timesMoved_thisYr, move_diff, move_description)
move_summary <- herd_move_difSimp %>%
  count(move_description) %>% 
  arrange(desc(n))
kable(move_summary)
```










